SecFFT: Safeguarding Federated Fine-tuning for Large Vision Language Models against Covert Backdoor Attacks in IoRT Networks

### 2024-11-15 response.tex

\textcolor{blue}{SecFFT outperforms other mechanisms in handling various attack. SecFFT achieves the lowest misidentification rate, at only 0.2\%, indicating its superior defense capability and robustness across various attack scenarios, accurately distinguishing between malicious and benign nodes. Conversely, the misidentification rates of Flame, FLTrust, and FoolsGold are 8\%, 3.9\%, and 9.5\%, respectively, with misidentified nodes more broadly distributed. Among them, FoolsGold exhibits the highest misidentification rate. It is worth noting that these statistical results align precisely with the findings from the previous experiment, further validating SecFFT's superior performance in instantaneous Attack Behavior Perception.}

Second, to improve the visibility and distinguish-ability of the partitioning results in Figure 6, we have added a supplementary sub-image that provides a clearer presentation of the partitioned sections. We also increased the font size to enhance readability, ensuring that key features are visible and easy to interpret. For details, please refer to Figure \ref{fig:lab1} and responses to the comment 2 from Reviewer 2.

Third, we re-adjusted the layout of Figure 7 to address the issues you pointed out. Specifically, we improved the font sizes, added necessary labels, and modified the legend for better comprehension. These adjustments were made to ensure that the experimental data in Figure 7 are both readable and visually clear. For details, please refer to Figure \ref{fig:lab2}.

% 修改后的结果如图\ref{fig:lab2}所示，同时我们也修改了文章中相应的分析部分，使其更易符合实验结果并且更易理解。
\begin{figure*}[!h]
    \centering
    \includegraphics[width=1\linewidth]{figures/lab2-combined.pdf}
    \caption{Visualization of node identification results under three attack scenarios (MR, EDGE CASE, NEUR) for four defense mechanisms (SecFFT, Flame, FLTrust, FoolsGold) using t-SNE. The F represent mis-identification, including both malicious nodes incorrectly identified as benign, or vice versa. }
    \label{fig:lab2}
\end{figure*}

% 对于Figure 7也是一样的，我们增加了对Figure 7的标题描述、文字分析等。

Similarly, for Figure 7, we have enhanced its description with a detailed caption, textual analysis, and additional explanations. This figure further illustrates the experimental outcomes across different defense methods under various attack scenarios. By providing a comprehensive breakdown of the visualized data and the implications of the results, we aim to ensure a clear understanding of the comparative performance of the algorithms. The improvements emphasize the nuances in the algorithms' behavior, highlighting their strengths and limitations under constrained and unconstrained conditions. The following are the corresponding modifications in the article:

% \textcolor{blue}{As shown in Figure \ref{fig:lab3}, the Foolsgold defense algorithm exhibits moderate performance against EdgeCase attacks. While it can generally identify similar behaviors among benign bot nodes, its effectiveness is limited. The size constraint does not affect the cosine similarity calculations, but with both size and angle constraints applied, Foolsgold fails to defend effectively. For the FLTrust defense algorithm, its performance against EdgeCase attacks slightly surpasses that of Foolsgold; however, a certain degree of similarity remains between malicious and benign bot nodes. The size constraint has no impact on FLTrust's defense, but the combined constraints of size and angle significantly weaken its effectiveness, rendering it unable to correctly identify malicious nodes. The Flame defense algorithm relies on the HDBSCAN clustering method for identification. During clustering, Flame assigns nearly identical (or even identical) scores to clients of the same category, resulting in heatmaps that appear uniform and visually clear. However, the clustering results are fundamentally flawed. For instance, in the figure, clients 25, 46, and 47 display streaks of different colors, which, although faint, indicate incorrectly classified bot nodes. In contrast, the SecFFT defense algorithm leverages similarity calculations based on intent points. Under EdgeCase attacks, SecFFT can accurately identify malicious bot nodes, while the similarity among benign bot nodes remains low. The size constraint has minimal impact on SecFFT's performance, and even with size and angle constraints applied, the algorithm maintains robust similarity classification and achieves perfect accuracy.}

\textcolor{blue}{As shown in Figure \ref{fig:lab3}, the Foolsgold defense algorithm shows moderate performance against EdgeCase attacks, but it can generally identify similar behaviors among benign bot nodes. The size constraint does not affect the cosine similarity results, but once both size and angle are constrained, Foolsgold fails to defend effectively. The metric used for Foolsgold in the plots is the $wv$ value from line 7 of Algorithm 1 in the original paper, which corresponds to the value in the author's open-source code.}

\textcolor{blue}{For FLTrust, its defense against EdgeCase attacks is slightly better than Foolsgold, but there is still some similarity between malicious and benign nodes. The size constraint has no impact on FLTrust's performance, but when both size and angle are constrained, its defense effectiveness declines significantly, making it unable to accurately identify malicious nodes. The metric for FLTrust is the $weights$ value from line 15 of Algorithm 2 in the original paper, corresponding to the result of applying the ReLU activation function to the cosine similarity of gradient changes between pairs of bot nodes in the author's open-source code.}

\textcolor{blue}{Flame uses HDBSCAN clustering for identification. The metric is the cluster probability ($Prob$) obtained after calling the HDBSCAN library function in the author's open-source code. While Flame assigns similar (or identical) scores to bot nodes of the same category, the clustering results are fundamentally flawed. For instance, bot nodes 25, 31, 32, and 34 are incorrectly identified as noise points rather than core or border points. This is due to HDBSCAN's hierarchical density clustering, which prioritizes the creation of stable clusters and merges points, classifying outliers with scores similar to benign bot nodes (e.g., 25, 31, 32, and 34) as noise.}

\textcolor{blue}{For SecFFT, the defense is based on intent-point similarity. Under EdgeCase attacks, SecFFT accurately identifies malicious bot nodes while showing low similarity among benign nodes. The size constraint has minimal impact on SecFFT's performance, and even with both size and angle constraints, SecFFT maintains strong similarity classification with perfect accuracy.}

\begin{figure*}[!t]
    \centering
    \includegraphics[width=\linewidth]{figures/lab3-combined.pdf}
    % \caption{攻击防御实验结果图。第一列到第四列分别代表防御方式Foolsgold、FLTrust、Flame和SecFFT，第一行到第三行分别代表攻击方式EdgeCase、限制大小的EdgeCase、限制大小和角度的EdgeCase。每个实验中有50个客户端，其中0-19号是恶意客户端，每个子图中颜色越红代表识别结果越相似，越蓝代表识别结果越不相似。第一列绘图依据是Foolsgold防御算法中基于余弦相似度计算出来的wv值，第二列绘图依据是FLTrust防御算法中依据余弦相似度和relu激活函数计算出来的聚合权重，第三列绘图依据是Flame算法聚类时所采用的HDBSCAN算法的评分，第四列绘图依据是我们提出的SecFFT算法依据意图点进行相似度计算得到的评分。虽然Flame算法看起来相同种类客户端之间分数较为类似，但实际上其聚类时有明显的聚类错误。}
    % \caption{\textcolor{red}{The experimental results of attack defense are illustrated in the figures. The first to fourth columns represent the defense methods \cite{foolsgold}, FLTrust\cite{FLTrust}, Flame\cite{FLAME}, and SecFFT, respectively, while the first to third rows represent the attack methods EdgeCase\cite{EDGE_CASE}, size-constrained EdgeCase, and EdgeCase constrained by both size and angle. Each experiment involves 50 clients, among which clients numbered 0–19 are malicious. In each subplot, the redder the color, the more similar the identification results, and the bluer the color, the less similar they are. The first column visualizes the results based on the wv values calculated using cosine similarity in the Foolsgold defense algorithm. The second column is based on the aggregation weights computed by the FLTrust defense algorithm using cosine similarity and the ReLU activation function. The third column visualizes scores obtained from the HDBSCAN algorithm used for clustering in the Flame defense method. The fourth column shows scores derived from the similarity calculation based on intent points in the proposed SecFFT algorithm. Although the Flame algorithm appears to produce more similar scores among the same type of clients, it exhibits evident clustering errors during its clustering process.}}
    % \caption{图中展示了四种防御方法（Foolsgold \cite{foolsgold}、FLTrust \cite{FLTrust}、Flame \cite{FLAME}、SecFFT）对三种攻击（EdgeCase \cite{EDGE_CASE}、大小限制的EdgeCase、同时限制大小和角度的EdgeCase）的防御效果。每个实验使用50个客户端（0-19为恶意客户端）。第一到三行分别代表EdgeCase攻击、限制大小的EdgeCase攻击和同时限制大小和角度的EdgeCase攻击。各列分别展示了基于余弦相似度（Foolsgold）、聚合权重（FLTrust）、HDBSCAN概率得分（Flame）和意图点相似度（SecFFT）的结果。}
    \caption{\textcolor{blue}{The figure illustrates the defense performance of four methods—Foolsgold \cite{foolsgold}, FLTrust \cite{FLTrust}, Flame \cite{FLAME}, and SecFFT—against three attack types: EdgeCase \cite{EDGE_CASE}, size-constrained EdgeCase, and EdgeCase constrained by both size and angle. Each experiment involves 50 clients, with clients 0-19 being malicious. The first to third rows represent EdgeCase attacks, size-constrained EdgeCase attacks, and EdgeCase attacks constrained by both size and angle, respectively. The columns show results based on cosine similarity (Foolsgold algorithm 1 line 7), aggregation weights (FLTrust algorithm 2 line 15), HDBSCAN probability scores (Flame Chapter 2.4), and intent-point similarity (SecFFT).}}
    \label{fig:lab3}
\end{figure*}

@@

\textcolor{blue}{
"Acc" refers to accuracy, which measures the proportion of correct predictions; "Rec" stands for recall, representing the model's ability to correctly identify positive instances; "FPR" denotes the false positive rate, indicating the proportion of negative instances incorrectly predicted as positive; "FNR" refers to the false negative rate, which represents the proportion of positive instances incorrectly predicted as negative; "AUC" stands for the area under the curve, reflecting the model's overall ability to distinguish between positive and negative instances; and "MCC" represents the Matthews correlation coefficient, which provides a balanced evaluation of the model's predictions.
}
%========================================================
% 表格2的内容太长，超出了双栏的空间了，建议重新进行调整规划
\rcomment{
\color{red} The content in Table 2 is too long and exceeds the space available for a two-column layout. Please revise and reformat accordingly.
}

% 我将每次给你一个审稿意见，请你对于该审稿意见写一个回复（回复要包括中文版本和英文版本）。回复要展现自己良好的态度，越详细越好。
% 你了解司法人工智能吗？请解释之。

% 谢谢你的建议，表格2的宽度确实有些过长，已经超出了半栏的范围，甚至已经与右侧栏目的内容产生了融合。我们对这个表格进行了调整，适当缩小了表格的宽度，使得表格在不影响整体观感的同时，保证了表格格式符合要求，且不超过单栏范围。
\textbf{Response:} 
Thank you for your suggestion. The width of Table 2 is indeed somewhat excessive, exceeding the single-column limit and even merging with the content in the adjacent column. We have made adjustments to the table, reducing its width appropriately to ensure that the table fits within the required format while maintaining the overall visual quality without exceeding the single-column range.

\begin{table}[h!]
\small
\centering
\caption{\textcolor{blue}{Metrics results with different attack and defense methods.}}
\resizebox{\columnwidth}{!}{%
\begin{tabular}{c|c|c|c|c|c|c|c}
\hline

\textcolor{blue}{Strategy} & \textcolor{blue}{Defense} & \textcolor{blue}{Acc.} & \textcolor{blue}{Rec.} & \textcolor{blue}{FPR} & \textcolor{blue}{FNR} & \textcolor{blue}{AUC} & \textcolor{blue}{MCC} \\ \hline

\multirow{4}{*}{\textcolor{blue}{None}} & \textcolor{blue}{Foolsgold} & \textcolor{blue}{0.96} & \textcolor{blue}{0.90} & \textbf{\textcolor{blue}{0.00}} & \textcolor{blue}{0.10} & \textcolor{blue}{0.95} & \textcolor{blue}{0.92} \\ 
                        & \textcolor{blue}{FLTrust}   & \textbf{\textcolor{blue}{1.00}} & \textbf{\textcolor{blue}{1.00}} & \textbf{\textcolor{blue}{0.00}} & \textbf{\textcolor{blue}{0.00}} & \textbf{\textcolor{blue}{1.00}} & \textbf{\textcolor{blue}{1.00}} \\ 
                        & \textcolor{blue}{Flame}     & \textcolor{blue}{0.92} & \textbf{\textcolor{blue}{1.00}} & \textcolor{blue}{0.13} & \textbf{\textcolor{blue}{0.00}} & \textcolor{blue}{0.93} & \textcolor{blue}{0.85} \\ 
                        & \textcolor{blue}{SecFFT}    & \textbf{\textcolor{blue}{1.00}} & \textbf{\textcolor{blue}{1.00}} & \textbf{\textcolor{blue}{0.00}} & \textbf{\textcolor{blue}{0.00}} & \textbf{\textcolor{blue}{1.00}} & \textbf{\textcolor{blue}{1.00}} \\ \hline

\multirow{4}{*}{\textcolor{blue}{Size}} & \textcolor{blue}{Foolsgold} & \textcolor{blue}{0.96} & \textcolor{blue}{0.90} & \textbf{\textcolor{blue}{0.00}} & \textcolor{blue}{0.10} & \textcolor{blue}{0.95} & \textcolor{blue}{0.92} \\ 
                        & \textcolor{blue}{FLTrust}   & \textbf{\textcolor{blue}{1.00}} & \textbf{\textcolor{blue}{1.00}} & \textbf{\textcolor{blue}{0.00}} & \textbf{\textcolor{blue}{0.00}} & \textbf{\textcolor{blue}{1.00}} & \textbf{\textcolor{blue}{1.00}} \\ 
                        & \textcolor{blue}{Flame}     & \textcolor{blue}{0.92} & \textbf{\textcolor{blue}{1.00}} & \textcolor{blue}{0.13} & \textbf{\textcolor{blue}{0.00}} & \textcolor{blue}{0.93} & \textcolor{blue}{0.85} \\ 
                        & \textcolor{blue}{SecFFT}    & \textbf{\textcolor{blue}{1.00}} & \textbf{\textcolor{blue}{1.00}} & \textbf{\textcolor{blue}{0.00}} & \textbf{\textcolor{blue}{0.00}} & \textbf{\textcolor{blue}{1.00}} & \textbf{\textcolor{blue}{1.00}} \\ \hline

\multirow{4}{*}{\textcolor{blue}{Angle}} & \textcolor{blue}{Foolsgold} & \textcolor{blue}{0.96} & \textcolor{blue}{0.90} & \textbf{\textcolor{blue}{0.00}} & \textcolor{blue}{0.10} & \textcolor{blue}{0.95} & \textcolor{blue}{0.92} \\ 
                        & \textcolor{blue}{FLTrust}   & \textbf{\textcolor{blue}{1.00}} & \textbf{\textcolor{blue}{1.00}} & \textbf{\textcolor{blue}{0.00}} & \textbf{\textcolor{blue}{0.00}} & \textbf{\textcolor{blue}{1.00}} & \textbf{\textcolor{blue}{1.00}} \\ 
                        & \textcolor{blue}{Flame}     & \textcolor{blue}{0.92} & \textbf{\textcolor{blue}{1.00}} & \textcolor{blue}{0.13} & \textbf{\textcolor{blue}{0.00}} & \textcolor{blue}{0.93} & \textcolor{blue}{0.85} \\ 
                        & \textcolor{blue}{SecFFT}    & \textbf{\textcolor{blue}{1.00}} & \textbf{\textcolor{blue}{1.00}} & \textbf{\textcolor{blue}{0.00}} & \textbf{\textcolor{blue}{0.00}} & \textbf{\textcolor{blue}{1.00}} & \textbf{\textcolor{blue}{1.00}} \\ \hline

\end{tabular}
}
\vspace{1em}
\begin{tablenotes}
\scriptsize
\item ``Acc." stands for Accuracy, ``Rec." for Recall, ``FPR" for False Positive Rate, ``FNR" for False Negative Rate, ``AUC" for Area Under Curve, and ``MCC" for Matthews Correlation Coefficient. The strategies are abbreviated as ``None" (EdgeCase without other strategies), ``Size" (Size-limited strategy), and ``Angle" (Angle-limited strategy).
\end{tablenotes}
\label{tab:detect}
\end{table}

### 2024-11-15 main-v2.tex
R1: 实验全部跑完
Signed-off-by: LetMeFly666 <814114971@qq.com>

% 后门检测主要旨在识别模型中已存在的后门攻击。在这一类中，SEER\cite{zhu2024seer}提出了一种用于视觉-语言模型的后门检测算法，通过在图像和文本模态的特征空间中联合搜索目标文本和图像触发器，成功实现了在多种场景下的后门检测。FoolsGold\cite{foolsgold}提出了一种通过检测各客户端更新的相似性来识别攻击者方法，该方法利用攻击者的更新通常更为相似这一特征自适应调整每个客户端的学习率，从而减少攻击者对模型训练的影响，有效防御投毒攻击，即使在存在大量恶意客户端的情况下也能显著降低攻击成功率。ASSET\cite{pan2023asset}提出了一种通过主动诱导后门样本和干净样本在模型行为上的差异，从而实现跨多种深度学习范式的鲁棒后门数据检测方法，并在端到端监督学习、自监督学习和迁移学习中表现出色。DECREE\cite{feng2023detecting}提出了一种用于检测自监督学习中预训练图像编码器后门的创新方法，该方法无需依赖标签数据或下游分类器，且在多种数据集和攻击类型下表现出极高的检测准确率。
\textbf{Backdoor Detection} primarily aims to identify existing backdoor attackers. In this category, FoolsGold\cite{foolsgold} proposes a method to identify attackers by detecting the similarity of updates from each client. This method adaptively adjusts the learning rate of each nodes based on the observation that the updates from attackers are usually more similar. It effectively defends against poisoning attacks and significantly lowers the attack success rate even with a large number of malicious nodes. ASSET \cite{pan2023asset} introduces a robust backdoor data detection method across multiple deep learning paradigms by actively inducing behavioral differences between backdoor and clean samples, demonstrating excellent performance in end-to-end supervised learning, self-supervised learning, and transfer learning. DECREE \cite{feng2023detecting} presents an innovative method for detecting backdoors in pre-trained image encoders used in self-supervised learning, achieving high detection accuracy across various datasets and attack types without relying on label data or downstream classifiers.

@@

% \textbf{Motivation}: 为了规避异常检测，有很多通过多轮次的组合攻击来植入后门的攻击。这些攻击很难在单轮次中检测出来，大致分为三类：1)限制大小的攻击，如\cite{geisler2024attacking, chen2024optimal}，这些攻击方法会限制单次攻击的大小，使得攻击并不是很明显，从而变得难以检测；2)限制角度的攻击，如\cite{you2023three, sagliano2024powered, dong2023adaptive}，这些攻击会限制每次攻击的角度，使其与正常的攻击类似从而变得难以识别；3)限制符号的攻击，如\cite{wan2023average, zhu2023boosting}，这些攻击通过梯度缩放或者梯度合成，控制恶意攻击的梯度与正常客户端梯度的正负维持一致，从而增加识别难度。本部分结合每个客户端的历史记录，通过识别攻击者最终的模型引导意图点来识别恶意节点。
\textbf{Motivation}: To evade anomaly detection systems, many backdoor attacks employ multi-round composite strategies that are difficult to detect in a single round. These attacks can be broadly classified into three types: (1) \textbf{Size-Limited Attacks} (e.g., \cite{geisler2024attacking, chen2024optimal}), which constrain the magnitude of each attack to make it subtle and less conspicuous, thereby reducing its detectability; (2) \textbf{Angle-Limited Attacks} (e.g., \cite{you2023three, sagliano2024powered, dong2023adaptive}), which restrict the direction of each attack so that it appears similar to legitimate updates, making them harder to recognize; and (3) \textbf{Sign-Limited Attacks} (e.g., \cite{wan2023average, zhu2023boosting}), which use techniques such as gradient scaling or gradient composition to ensure that the signs of the malicious gradients align with those of legitimate clients, thereby increasing the difficulty of detection. This section presents an approach that leverages each client's historical records to identify malicious nodes by analyzing their ultimate intent to manipulate the global model.

@@

\textbf{Overview}: The previous defense algorithms have effectively identified single-round attacks; this section focuses on leveraging clients' historical records for effective identification. We maintain the global models $\theta_g^{t'}$ from the past $T$ rounds, where $\max\{t-T+1, 1\}\leq t'\leq t$, and consider their flattened versions as points in a high-dimensional space. Simultaneously, we keep track of each client's historical updates, viewing them as vectors in the high-dimensional space and extending them as rays. For each client, we use the Minimum Enclosing Ball algorithm to compute a minimal hypersphere that covers a $\zeta$ proportion of the ray. The final position of the hypersphere's center can be regarded as the intended steering point of the global model for the corresponding node, and the radius of the hypersphere can be regarded as the reliability level.

@@

% 像正常的联邦学习过程一样，中央服务器每次下发一个全局模型，每个客户端得到全局模型后使用本地数据进行训练，并将更新变化上传到中央服务器中。我们将第$t$轮次的全局模型记为$\theta_t$，将客户端$i$第$t$轮次训练后的模型记为$\theta^t_i$。客户端$i$将训练后的模型$\theta^t_{i}$减去训练前中央服务器下发的全局模型$\theta^t$，就得到了$t$轮次的更新变化$\triangledown \theta^t_{i}=\theta^t_{i}-\theta^t$。客户端将更新变化$\triangledown \theta^t_{i}$上传到中央服务器，中央服务器在聚合的同时，记录下每个客户端当前轮次的更新$\triangledown \theta^t_{i}$展平后的结果$\bar{\theta_i^t}$，同时存下中央服务器上轮次下发的全局模型$\theta^{t-1}$。中央服务器最多保留$T$轮次的模型和更新历史记录。“Keep T-rounds History”的主要算法过程如算法\ref{alg:malicious-node-detection-history}的3-13行所示。
As in a typical federated learning process, the central server distributes a global model in each round. Upon receiving the global model, each client trains on its local data and uploads the updates to the central server. Let the global model in the $t$-th round be denoted as $\theta_t$, and the model of client $i$ after training in the $t$-th round be denoted as $\theta^t_i$. Client $i$ computes its update in the $t$-th round as the difference between the trained model $\theta^t_{i}$ and the global model received before training $\theta^t$, i.e., $\triangledown \theta^t_{i} = \theta^t_{i} - \theta_g^t$. The client uploads the update $\triangledown \theta^t_{i}$ to the central server. While aggregating, the central server records the flattened result of each client's update in the current round, $\bar{\theta_i^t}$, as well as the global model $\theta^{t-1}$ distributed by the central server in the previous round. The central server retains the models and weights update histories for up to $T$ rounds.% The main algorithm process for "Keep T-rounds History" is shown in lines 3-13 of Algorithm \ref{alg:malicious-node-detection-history}.

\subsubsection{Construction of attack intention}
% 这个问题可以抽象为高维空间中的一些具有起点的射线。射线的起点代表上轮次的全局模型，射线的方向代表本轮次展平后的更新变化。问题的优化目标是：找到一个最小的超球，至少覆盖$\zeta$比例的射线。
This problem can be abstracted as rays in a high-dimensional space with specific starting points. The starting point of a ray represents the global model from the previous round, and the direction of the ray represents the flattened update in the current round. The optimization goal of the problem is to find a minimum hypersphere that covers at least a $\zeta$ proportion of the rays. \textcolor{red}{Among them, $\ zeta $is to avoid interference from excessively outlier rays}.
% 我们使用符号$O_i$代表客户端$i$在高维空间中超球的球心，使用符号$r_i$代表这个超球的半径。假设当前轮次为$t$，$t'$是最近$T$轮次中的其中一轮，使用符号$\tilde O_i^{t'}$代表球心到第$t'$对应射线的最近点。则可以定义优化问题：
We use the symbol $O_i$ to represent the center of the hypersphere for client $i$ in the high-dimensional space and $r_i$ to represent the radius of this hypersphere. Suppose the current round is $t$, and $t'$ is one of the recent $T$ rounds. Let $\tilde O_i^{t'}$ denote the closest point from the hypersphere center to the ray corresponding to round $t'$. Then, the optimization problem can be defined as:

\begin{equation}
    \min_{O_i, r_i} \quad r_i
\end{equation}

\begin{equation} 
\text{s.t.} \quad \left| \left\{ t' \mid \| O_i - \tilde{O}_{i}^{t'} \| \leq r_i \right\} \right| \geq \zeta T,
\end{equation}
\begin{equation} 
    \quad\quad\max\{t-T+1, 1\}\leq  t'\leq t.
\end{equation}
% “Obtain the Purpose Intention”的主要算法过程如算法\ref{alg:malicious-node-detection-history}的14-18行所示。此部分又可以分为“Construct Ray Model”和“Minimum Enclosing Hypersphere Calculation”两部分。
%The main algorithm process for "Obtain the Purpose Intention" is shown in lines 14-18 of Algorithm \ref{alg:malicious-node-detection-history}. This section can be further divided into two parts: "Construct Ray Model" and "Minimum Enclosing Hypersphere Calculation."
% “Construct Ray Model”的主要过程如下。对于每个客户端 \(R_i\)，中央服务器保留了最近 \(T\) 轮的全局模型历史以及每轮次的更新变化历史。设 \( \theta_g^{t-T}, \theta_g^{t-T+1}, \dots, \theta_g^{t-1} \) 是最近 \(T\) 轮次的全局模型，且这些全局模被“展平”到了高维空间中的一个点。类似地，设 \( \overline{\triangledown\theta_{i}^{t-T}}, \overline{\triangledown\theta_{i}^{t-T+1}}, \dots, \overline{\triangledown\theta_{i}^{t-1}} \) 是最近 \(T\) 轮次客户端 \(i\) 上传的展平后的梯度变化向量。

>>>>

% 后门检测主要旨在识别模型中已存在的后门攻击。在这一类中，SEER\cite{zhu2024seer}提出了一种用于视觉-语言模型的后门检测算法，通过在图像和文本模态的特征空间中联合搜索目标文本和图像触发器，成功实现了在多种场景下的后门检测。FoolsGold\cite{foolsgold}提出了一种通过检测各客户端更新的相似性来识别攻击者方法，该方法利用攻击者的更新通常更为相似这一特征自适应调整每个客户端的学习率，从而减少攻击者对模型训练的影响，有效防御投毒攻击，即使在存在大量恶意客户端的情况下也能显著降低攻击成功率。ASSET\cite{pan2023asset}提出了一种通过主动诱导后门样本和干净样本在模型行为上的差异，从而实现跨多种深度学习范式的鲁棒后门数据检测方法，并在端到端监督学习、自监督学习和迁移学习中表现出色。DECREE\cite{feng2023detecting}提出了一种用于检测自监督学习中预训练图像编码器后门的创新方法，该方法无需依赖标签数据或下游分类器，且在多种数据集和攻击类型下表现出极高的检测准确率。
\textbf{Backdoor Detection} primarily aims to identify existing backdoor attackers. In this category, FoolsGold\cite{foolsgold} proposes a method to identify attackers by detecting the similarity of updates from each node. This method adaptively adjusts the learning rate of each nodes based on the observation that the updates from attackers are usually more similar. It effectively defends against poisoning attacks and significantly lowers the attack success rate even with a large number of malicious nodes. ASSET \cite{pan2023asset} introduces a robust backdoor data detection method across multiple deep learning paradigms by actively inducing behavioral differences between backdoor and clean samples, demonstrating excellent performance in end-to-end supervised learning, self-supervised learning, and transfer learning. DECREE \cite{feng2023detecting} presents an innovative method for detecting backdoors in pre-trained image encoders used in self-supervised learning, achieving high detection accuracy across various datasets and attack types without relying on label data or downstream classifiers.

@@

% \textbf{Motivation}: 为了规避异常检测，有很多通过多轮次的组合攻击来植入后门的攻击。这些攻击很难在单轮次中检测出来，大致分为三类：1)限制大小的攻击，如\cite{geisler2024attacking, chen2024optimal}，这些攻击方法会限制单次攻击的大小，使得攻击并不是很明显，从而变得难以检测；2)限制角度的攻击，如\cite{you2023three, sagliano2024powered, dong2023adaptive}，这些攻击会限制每次攻击的角度，使其与正常的攻击类似从而变得难以识别；3)限制符号的攻击，如\cite{wan2023average, zhu2023boosting}，这些攻击通过梯度缩放或者梯度合成，控制恶意攻击的梯度与正常客户端梯度的正负维持一致，从而增加识别难度。本部分结合每个客户端的历史记录，通过识别攻击者最终的模型引导意图点来识别恶意节点。
\textbf{Motivation}: To evade anomaly detection systems, many backdoor attacks employ multi-round composite strategies that are difficult to detect in a single round. These attacks can be broadly classified into three types: (1) \textbf{Size-Limited Attacks} (e.g., \cite{geisler2024attacking, chen2024optimal}), which constrain the magnitude of each attack to make it subtle and less conspicuous, thereby reducing its detectability; (2) \textbf{Angle-Limited Attacks} (e.g., \cite{you2023three, sagliano2024powered, dong2023adaptive}), which restrict the direction of each attack so that it appears similar to legitimate updates, making them harder to recognize; and (3) \textbf{Sign-Limited Attacks} (e.g., \cite{wan2023average, zhu2023boosting}), which use techniques such as gradient scaling or gradient composition to ensure that the signs of the malicious gradients align with those of legitimate nodes, thereby increasing the difficulty of detection. This section presents an approach that leverages each node's historical records to identify malicious nodes by analyzing their ultimate intent to manipulate the global model.

@@

\textbf{Overview}: The ``Instantaneous Attack Behavior Perception" mechanism is effective in identifying single-round attacks, however, it performs poorly when addressing stealthy multi-round composite attacks. Consequently, this section focuses on utilizing the historical updates to effectively identify malicious nodes. We maintain the global models $\theta_g^{t'}$ from the past $T$ rounds, where $\max\{t-T+1, 1\}\leq t'\leq t$, and consider flattened global model as a point in a high-dimensional space. 
Simultaneously, the historical updates of each node are recorded and represented as vectors in the same high-dimensional space, which are then extended into rays.
% Simultaneously, we keep track of each client's historical updates, viewing them as vectors in the high-dimensional space and extending them as rays. 
% For each client, we use the Minimum Enclosing Ball algorithm to compute a minimal hypersphere that covers a $\zeta$ proportion of the ray. The final position of the hypersphere's center can be regarded as the intended steering point of the global model for the corresponding node, and the radius of the hypersphere can be regarded as the reliability level.
For each node, the ``Minimum Enclosing Hypersphere Ball (MEHB)" is applied to compute the smallest hypersphere that covers a 
$\zeta$-proportion of the rays. The center of the hypersphere can be interpreted as the intended guiding point of the node for the global model, while the radius of the hypersphere reflects the confidence level of the corresponding node.

@@

% 像正常的联邦学习过程一样，中央服务器每次下发一个全局模型，每个客户端得到全局模型后使用本地数据进行训练，并将更新变化上传到中央服务器中。我们将第$t$轮次的全局模型记为$\theta_t$，将客户端$i$第$t$轮次训练后的模型记为$\theta^t_i$。客户端$i$将训练后的模型$\theta^t_{i}$减去训练前中央服务器下发的全局模型$\theta^t$，就得到了$t$轮次的更新变化$\triangledown \theta^t_{i}=\theta^t_{i}-\theta^t$。客户端将更新变化$\triangledown \theta^t_{i}$上传到中央服务器，中央服务器在聚合的同时，记录下每个客户端当前轮次的更新$\triangledown \theta^t_{i}$展平后的结果$\bar{\theta_i^t}$，同时存下中央服务器上轮次下发的全局模型$\theta^{t-1}$。中央服务器最多保留$T$轮次的模型和更新历史记录。“Keep T-rounds History”的主要算法过程如算法\ref{alg:malicious-node-detection-history}的3-13行所示。
Similar to the standard federated learning process, the central server distributes a global model in each round. After receiving the global model, each node trains it using local data and uploads the updates to the central server. Let the global model in round $t$ be denoted as $\theta^{t-1}_g$, and the model trained by node $i$ in round $t$ be denoted as $\theta^t_i$. The update from node $i$ in round $t$ is calculated as $\triangledown \theta^t_{i} = \theta^t_{i} - \theta^{t-1}_g$. 
While aggregating the updates, the central server records the flattened update $\bar{\theta_i^t}$ of each node and stores the global model $\overline{\theta_g^{t-1}}$. The central server maintains the history of models and updates for up to $T$ rounds. 
Therefore, let \( \overline{\theta_g^{t-T}}, \overline{\theta_g^{t-T+1}}, \dots, \overline{\theta_g^{t-1}} \) denote the flattened global models and \( \overline{\triangledown\theta_{i}^{t-T}}, \overline{\triangledown\theta_{i}^{t-T+1}}, \dots, \overline{\triangledown\theta_{i}^{t-1}} \) denote the flattened update uploaded by node \(i\) from the past \(T\) rounds.

% As in a typical federated learning process, the central server distributes a global model in each round. Upon receiving the global model, each client trains on its local data and uploads the updates to the central server. Let the global model in the $t$-th round be denoted as $\theta_g^t$, and the model of client $i$ after training in the $t$-th round be denoted as $\theta^t_i$. Client $i$ computes its update in the $t$-th round as the difference between the trained model $\theta^t_{i}$ and the global model received before training $\theta^t$, i.e., $\triangledown \theta^t_{i} = \theta^t_{i} - \theta_g^t$. The client uploads the update $\triangledown \theta^t_{i}$ to the central server. While aggregating, the central server records the flattened result of each client's update in the current round, $\bar{\theta_i^t}$, as well as the global model $\theta^{t-1}$ distributed by the central server in the previous round. The central server retains the models and weights update histories for up to $T$ rounds.% The main algorithm process for "Keep T-rounds History" is shown in lines 3-13 of Algorithm \ref{alg:malicious-node-detection-history}.

\subsubsection{Construction of attack intention}
% 这个问题可以抽象为高维空间中的一些具有起点的射线。射线的起点代表上轮次的全局模型，射线的方向代表本轮次展平后的更新变化。问题的优化目标是：找到一个最小的超球，至少覆盖$\zeta$比例的射线。
% This problem can be abstracted as rays in a high-dimensional space with specific starting points. The starting point of a ray represents the global model from the previous round, and the direction of the ray represents the flattened update in the current round. The optimization goal of the problem is to find a minimum hypersphere that covers at least a $\zeta$ proportion of the rays. \textcolor{red}{Among them, $\ zeta $is to avoid interference from excessively outlier rays}.
% 我们使用符号$O_i$代表客户端$i$在高维空间中超球的球心，使用符号$r_i$代表这个超球的半径。假设当前轮次为$t$，$t'$是最近$T$轮次中的其中一轮，使用符号$\tilde O_i^{t'}$代表球心到第$t'$对应射线的最近点。则可以定义优化问题：
% We use the symbol $O_i$ to represent the center of the hypersphere for client $i$ in the high-dimensional space and $r_i$ to represent the radius of this hypersphere. Suppose the current round is $t$, and $t'$ is one of the recent $T$ rounds. Let $\tilde O_i^{t'}$ denote the closest point from the hypersphere center to the ray corresponding to round $t'$. Then, the optimization problem can be defined as:

This problem can be abstracted as finding a smallest hypersphere that covers at least $\zeta$-proportion of a set of rays in a high-dimensional space, each with a defined starting point. The starting point of a ray is the flattened global model in the round $t'-1$, and the direction of the ray corresponds to the flattened update from node $R_i$ in the round $t'$, where $\max\{t-T+1, 1\}\leq t'\leq t$. Equation \ref{eq:ray} is the corresponding ray equation, where $\alpha\in [0, +\infty)$ is the parameter of the ray. 
We use the symbol $O_i$ to denote the center of the hypersphere for node $i$ in the high-dimensional space, the symbol $r_i$ to denote the radius of this hypersphere and the symbol $\tilde{O}_i^{t'}$ to denote the nearest point from the hypersphere center to the ray corresponding to round $t'$. Thus, the optimization problem can then be defined as Equation \ref{eq:optimization}.

\begin{equation}
l_i^{t'}=Flatten(\theta_g^{t'-1}) + \alpha \overline{\triangledown\theta_{i}^{t'}},
\label{eq:ray}
\end{equation}
